Prognostic and biological relevance of collagen-related genes in prostate cancer

### 2025-02-25 paper/markdown/manuscript_figures_tables.Rmd
Methods for the main manuscript
ROC analysis for BCR is still pernding

Seven publicly available transcriptome data sets of primary prostate cancer samples, 
the TCGA prostate cancer cohort [@Liu2018; @Abeshouse2015] (n = `r tcga$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples, RNA sequencing), 
GSE16560 [@Sboner2010] (n = `r gse16560$expression %>% filter(tissue_type == 'tumor') %>% nrow`, microarray)
GSE54460 [@Long2014] (n = `r gse54460$expression %>% filter(tissue_type == 'tumor') %>% nrow`, RNA sequencing), 
GSE70768  [@Ross-Adams2015] (n = `r gse70768$expression %>% filter(tissue_type == 'tumor') %>% nrow`, microarray), 
GSE70769  [@Ross-Adams2015] (n = `r gse70769$expression %>% filter(tissue_type == 'tumor') %>% nrow`, microarray), 
GSE220095 [@Schimmelpfennig2023] (n = `r gse220095$expression %>% filter(tissue_type == 'tumor') %>% nrow`, RNA sequencing), and 
DKFZ [@Gerhauser2018] (n = `r dkfz$expression %>% filter(tissue_type == 'tumor') %>% nrow`, RNA sequencing) 
were re-analyzed. 
Selection criteria for the transcriptomic cohorts were: information of biochemical relapse and relapse-free survival or death and overall survival, and availability of expression data for `r nrow(globals$genes_interest)` collagen-related transcript investigated in our previous collagen project [@Heidegger2024].

@@

@@

## Multi-parameter modeling of BCR-free and overall survival

@@

Publicly available data sets were analyzed. 
Formatted data sets used for analyses will be made available upon request to the corresponding author. 
The R analysis pipeline for the transcriptome data is available from GitHub (https://github.com/PiotrTymoszuk/BCR_collagen).

@@

_HR with 95% confidence intervals for BCR risk in the high versus low expression strata are presented in a Forest plot (left). The model performance statistics, Harrell's concordance index (C-index, measure of model accuracy), and Integrated Brier Scores (IBS, measure of overall model calibration, low values indicative of good calibration) are presented in a dot plot (right)._

@@

_(A) Metrics of performance of the survival models, Harrell's concordance index (C-index, measure of model accuracy) and Integrated Brier Score (IBS, measure of overall model calibration, low values are characteristic for good calibration), are presented in dot plots. Dashed lines represent C-index and IBS values expected for random BCR risk prediction. Note the superior accuracy and calibration of the GBM model in the validation collectives._

>>>>

Seven publicly available transcriptome data sets of primary prostate cancer samples, 
the [TCGA](https://www.cbioportal.org/study/summary?id=prad_tcga_pan_can_atlas_2018) prostate cancer cohort [@Liu2018; @Abeshouse2015] (n = `r tcga$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples, RNA sequencing), 
[GSE16560](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE16560) [@Sboner2010] (n = `r gse16560$expression %>% filter(tissue_type == 'tumor') %>% nrow`, microarray)
[GSE54460](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE54460) [@Long2014] (n = `r gse54460$expression %>% filter(tissue_type == 'tumor') %>% nrow`, RNA sequencing), 
[GSE70768](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE70768) [@Ross-Adams2015] (n = `r gse70768$expression %>% filter(tissue_type == 'tumor') %>% nrow`, microarray), 
[GSE70769](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE70769) [@Ross-Adams2015] (n = `r gse70769$expression %>% filter(tissue_type == 'tumor') %>% nrow`, microarray), 
[GSE220095](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE220095) [@Schimmelpfennig2023] (n = `r gse220095$expression %>% filter(tissue_type == 'tumor') %>% nrow`, RNA sequencing), and 
[DKFZ](https://www.cbioportal.org/study/summary?id=prostate_dkfz_2018) [@Gerhauser2018] (n = `r dkfz$expression %>% filter(tissue_type == 'tumor') %>% nrow`, RNA sequencing) 
were re-analyzed. 
Selection criteria for the transcriptomic cohorts were: information of biochemical relapse and relapse-free survival or death and overall survival, and availability of expression data for `r nrow(globals$genes_interest)` collagen-related transcript investigated in our previous collagen project [@Heidegger2024].

@@

Co-expression networks of the collagen-related transcripts were constructed in the poled GEO, DKFZ, and TCGA cohorts. 
The networks' edges were defined by pairwise correlations of the ComBat-adjusted $log_2$ expression levels with Spearman's $\rho \geq$ 0.5; transcripts without any network neighbors were removed. 
Importance of the network's vertices, i.e. the collagen-related transcripts, was assessed by 
degree as a measure of connectivity (number of neighbors), 
hub score as a metric of overall correlation strength (eigenvector of the affinity matrix), 
betweenness as a measure of connectivity and centrality (minimum/maximum-scaled number of the shortest paths between all pairs of vertices that pass through the vertex of interest), and 
transitivity (fraction of neighbor vertices that are connected with each other) [@Csardi2006] (__Supplementary Table S5__).

@@

For univariable analysis of BCR-free survival, PCA patients in the pooled GEO, TCGA, and DKFZ cohort were classified as high and low expressors of each collagen-related gene with a cutoffs corresponding to the largest difference in survival between the expression strata. 
BCR risk of the high as compared with low expressors was assessed by unavailable Cox proportional hazard regression. 
Inference of the Cox proportional hazard models was assessed by hazard ratio (HR) with 95% confidence intervals, and p values corrected for multiple testing with the false discovery rate method (FDR). 
Harrell's concordance index [@Harrell1996] and Integrated Brier Score [@Graf1999] were used as statistics of, respectively, model accuracy and calibration (__Supplementary Table S6__).

## Multi-parameter modeling of BCR-free survival

Machine learning models of BCR-free survival were constructed for the following sets of explanatory variables: 
(1) first- and second-order terms of ComBat-adjusted $log_2$ expression levels of the collagen-related transcripts, 
(2) pathological tumor stage, ISUP grade, and ComBat-adjusted $log_2$ mRNA levels of the PSA-coding gene _KLK3_ [@Lunger2021; @Boyukozer2020] as clinical predictors of BCR, and 
(3) pathological tumor stage, ISUP grade, ComBat-adjusted $log_2$ _KLK3_ mRNA levels, as well as the first- and second-order terms of ComBat-adjusted $log_2$ expression levels of the collagen-related transcripts. 
The models were trained in the pooled GEO cohort with six algorithms (RIDGE regularized Cox proportional hazard regression, Elastic Net regularized Cox proportional hazard regression, LASSO regularized Cox proportional hazard regression, Support Vector Machines [SVM], Random Forest, and Gradient Boosted Machines [GBM]) [@Simon2011; @Tibshirani1996; @Zou2005; @Friedman2010; @Fouodo2018; @Weston1998; @Breiman2001; @Ishwaran2008; @Friedman2001; @Greenwell2022; @Friedman2002]. 
Performance of the models was evaluated by comparison of the predicted and actual BCR-free survival in the pooled GEO training cohort, and TCGA and DKFZ validation collectives with Harrell's concordance index and Integrated Brier Scores (__Supplementary Tables S7__ - __S8__). 
Additionally, BCR-free survival in patients stratified by tertiles of predictor scores returned by the machine learning models was explored with Kaplan-Meier plots and Peto-Peto tests. 
Finally, confidence and calibration of the models was assessed by plots of Brier Scores for unique follow-up times.

## Multi-parameter modeling of overall survival

Overall survival of PCA patients was modeled in the GSE16560 watchful waiting cohort [@Sboner2010]. 
First- and second-order terms of ComBat-adjusted $log_2$-transformed expression levels of the collagen-related genes served as explanatory factors. 
Machine learning models using the algorithms outlined above for the BCR-free survival were trained in a training subset of the GSE16560 cohort, and validated in the test subset. 
Performance of the models of overall survival was evaluated in the training and test subsets of the GSE16560 cohort as described above for BCR-free survival (__Supplementary Tables S9__ - __S10__).

@@

Publicly available data sets were analyzed: the links are provided in __Methods/Transcriptome data sets__. 
Formatted data sets used for analyses will be made available upon request to the corresponding author. 
The R analysis pipeline for the transcriptome data is available from GitHub (https://github.com/PiotrTymoszuk/BCR_collagen).

@@

_HR with 95% confidence intervals for BCR risk in the high versus low expression strata are presented in a Forest plot (left). The model performance statistics, Harrell's concordance index (C-index, measure of model accuracy), and Integrated Brier Scores (IBS, measure of model calibration, low values indicative of good calibration) are presented in a dot plot (right)._

@@

_(A) Metrics of performance of the survival models, Harrell's concordance index (C-index, measure of model accuracy) and Integrated Brier Score (IBS, measure of model calibration, low values are characteristic for good calibration), are presented in dot plots. Dashed lines represent C-index and IBS values expected for random BCR risk prediction. Note the superior accuracy and calibration of the GBM model in the validation collectives._

### 2025-02-25 paper/markdown/manuscript_supplement.Rmd
Methods for the main manuscript
ROC analysis for BCR is still pernding

The TCGA prostate cancer data set [@Liu2018; @Abeshouse2015] and DKFZ data set [@Gerhauser2018] consisted of normalized RNA sequencing data for `r tcga$expression %>% filter(tissue_type == 'tumor') %>% nrow` and `r dkfz$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples, respectively, with accompanying clinical information and were obtained from the cBioportal repository with in-house-developed R scripts.

The GSE16560 [@Sboner2010] (microarray, Human 6k Transcriptionally Informative Gene Panel for DASL, n = `r gse16560$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples), 
GSE54460 [@Long2014] (RNA sequencing, n = `r gse54460$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples), 
GSE70768 [@Ross-Adams2015] (Illumina HumanHT-12 V4.0 expression beadchip microarray, n = `r gse70768$expression %>% filter(tissue_type == 'tumor') %>% nrow`), 
GSE70769 [@Ross-Adams2015] (Illumina HumanHT-12 V4.0 expression beadchip microarray, n = `r gse70769$expression %>% filter(tissue_type == 'tumor') %>% nrow`), and 
GSE220095 [@Schimmelpfennig2023] (RNA sequencing, n = `r gse220095$expression %>% filter(tissue_type == 'tumor') %>% nrow`) data sets with normalized whole-transcriptome and basic clinical information were fetched from GEO with the `getGEO()` function from the _GEOquery_ package.

@@

BCR risk in the high expressors as compared with the low expressors for each of the collagen-related transcripts was modeled by univariable Cox proportional hazard regression (function `coxph()` and `as_coxex()`, packages _survival_ and [_coxExtensions_](https://github.com/PiotrTymoszuk/coxExtensions)) [@Therneau2000]. 
Hazard ratios (HR) for BCR risk in the high as compared with low expressors with 95% confidence intervals served as the inference statistics of the models. 
The inference p values ($p(HR = 1)$), were corrected for multiple testing with the FDR method. 
Accuracy of the model was assessed by 
Harrell's concordance index [@Harrell1996] (high values are characteristic for high concordance between the predicted and observed BCR risk),  
overall model calibration and confidence of predictions was gauged by Integrated Brier Score (low values are expected for well calibrated and highly confident models) [@Graf1999]. 
The inference and model fit metrics were computed by calling `summary()` method from [_coxExtensions_](https://github.com/PiotrTymoszuk/coxExtensions) for the model objects. 
Genes found to be associated with unfavorable (pFDR < 0.05, HR > 1) or favorable BCR prognosis (pFDR < 0.05, HR < 1) in all three cohorts were considered as standalone markers of BCR prognosis listed in __Supplementary Table S\@ref(tab:tab-uni-bcr)__.

@@

suppl_tab$uni_bcr %>% 
  filter(`Gene symbol` %in% reduce(uni_cut$common_significant, union)) %>% 
  arrange(`Association with BCR risk`, `Gene symbol`, Cohort) %>% 
  relocate(`Association with BCR risk`, `Gene symbol`, Cohort) %>% 
  flextable %>% 
  merge_v(1:2) %>% 
  italic(j = 2) %>% 
  set_widths(c(2, 2, 2, 1.8, rep(2.4, 2), 2.2, 2.3, rep(1.7, 2))) %>% 
  footnote(1, 7, 
           value = as_paragraph('Harazd ratio (HR) with 95% confidence intervals (CI).'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 9, 
           value = as_paragraph("C-index: Harrel's concordance index, a measure of model accuracy. High values are expected for a highly accurate model; concordance index = 0.5 is expected for random predictions."), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  footnote(1, 10, 
           value = as_paragraph('IBS: Integrated Brier Score, a metric of overall model calibration. Low values are expected for a well calibrate model. Intergrated Brier score = 0.25 is expected for random predictions.'), 
           part = 'header', 
           ref_symbols = 'c') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tab$bcr_eval) %>% 
  merge_v(1:2) %>% 
  set_widths(c(3.5, 2.7, 3.5, rep(2.5, 2))) %>% 
   footnote(1, 1, 
           value = as_paragraph('SVM: Support Vector Machines; GBM: Gradient Boosted Machines.'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1:18, 1, 
           value = as_paragraph('Explanatory factors: expression levels of the collagen-related transcripts.'), 
           part = 'body', 
           ref_symbols = 'b') %>% 
  footnote(19:21, 1, 
           value = as_paragraph('Explanatory factors: pathological tumor stage, ISUP grade, and log2 expression of the PSA coding gene KLK3 in the tumor tissue.'), 
           part = 'body', 
           ref_symbols = 'c') %>% 
   footnote(22:24, 1, 
           value = as_paragraph('Explanatory factors: pathological tumor stage, ISUP grade, and log2 expression of the PSA coding gene KLK3 in the tumor tissue, log2 expression of the collagen-related transcripts.'), 
           part = 'body', 
           ref_symbols = 'd') %>% 
  footnote(1, 4, 
           value = as_paragraph("C-index: Harrel's concordance index, a measure of model accuracy. High values are expected for a highly accurate model; concordance index = 0.5 is expected for random predictions."), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  footnote(1, 5, 
           value = as_paragraph('IBS: Integrated Brier Score, a metric of overall model calibration. Low values are expected for a well calibrated model. Intergrated Brier score = 0.25 is expected for random predictions.'), 
           part = 'header', 
           ref_symbols = 'c') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tab$os_eval) %>% 
  set_widths(c(3.5, 2.7, rep(2.5, 2))) %>% 
  merge_v(1) %>% 
  footnote(1, 3, 
           value = as_paragraph("C-index: Harrell's concordance index, a measure of model accuracy. High values are expected for a highly accurate model; concordance index = 0.5 is expected for random predictions."), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  footnote(1, 4, 
           value = as_paragraph('IBS: Integrated Brier Score, a metric of overall model calibration. Low values are expected for a well calibrate model. Intergrated Brier score = 0.25 is expected for random predictions.'), 
           part = 'header', 
           ref_symbols = 'c') %>% 
  theme_vanilla

@@

_(A) Numeric metrics of survival model performance, Harrell's concordance index (C-index, measure of model accuracy) and Integrated Brier Score (IBS, measure of overall calibration, low values are characteristic for well calibrated models), are presented in a dot plot. Each point represents a single GBM model, point color codes for the model type. Models in the same cohort are connected with lines. Note the substantial improvement of the GBM model accuracy and calibration upon inclusion of the collagen-related transcript expression levels in the explanatory variable set in the pooled GEO and DKFZ cohorts._

@@

_(A) Metrics of performance of the survival models, Harrell's concordance index (C-index, measure of model accuracy) and Integrated Brier Score (IBS, measure of overall model calibration, low values are characteristic for good calibration), are presented in dot plots. Dashed lines represent C-index and IBS values expected for random death risk prediction. Note the superior accuracy and calibration of the GBM model in the validation collectives._

>>>>

The [TCGA](https://www.cbioportal.org/study/summary?id=prad_tcga_pan_can_atlas_2018) prostate cancer data set [@Liu2018; @Abeshouse2015] and [DKFZ](https://www.cbioportal.org/study/summary?id=prostate_dkfz_2018) data set [@Gerhauser2018] consisted of normalized RNA sequencing data for `r tcga$expression %>% filter(tissue_type == 'tumor') %>% nrow` and `r dkfz$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples, respectively, with accompanying clinical information and were obtained from the cBioportal repository with in-house-developed R scripts.

The [GSE16560](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE16560) [@Sboner2010] (microarray, Human 6k Transcriptionally Informative Gene Panel for DASL, n = `r gse16560$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples), 
GSE54460(https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE54460) [@Long2014] (RNA sequencing, n = `r gse54460$expression %>% filter(tissue_type == 'tumor') %>% nrow` cancer samples), 
[GSE70768](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE70768) [@Ross-Adams2015] (Illumina HumanHT-12 V4.0 expression beadchip microarray, n = `r gse70768$expression %>% filter(tissue_type == 'tumor') %>% nrow`), 
[GSE70769](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE70769) [@Ross-Adams2015] (Illumina HumanHT-12 V4.0 expression beadchip microarray, n = `r gse70769$expression %>% filter(tissue_type == 'tumor') %>% nrow`), and 
[GSE220095](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE220095) [@Schimmelpfennig2023] (RNA sequencing, n = `r gse220095$expression %>% filter(tissue_type == 'tumor') %>% nrow`) data sets with normalized whole-transcriptome and basic clinical information were fetched from GEO with the `getGEO()` function from the _GEOquery_ package.

@@

BCR risk in the high expressors as compared with the low expressors for each of the collagen-related transcripts was modeled by univariable Cox proportional hazard regression (function `coxph()` and `as_coxex()`, packages _survival_ and [_coxExtensions_](https://github.com/PiotrTymoszuk/coxExtensions)) [@Therneau2000]. 
Hazard ratios (HR) for BCR risk in the high as compared with low expressors with 95% confidence intervals served as the inference statistics of the models. 
The inference p values ($p(HR = 1)$), were corrected for multiple testing with the FDR method. 
Accuracy of the model was assessed by 
Harrell's concordance index [@Harrell1996] (high values are characteristic for high concordance between the predicted and observed BCR risk),  
model calibration and confidence of predictions was gauged by Integrated Brier Score (low values are expected for well calibrated and highly confident models) [@Graf1999]. 
The inference and model fit metrics were computed by calling `summary()` method from [_coxExtensions_](https://github.com/PiotrTymoszuk/coxExtensions) for the model objects. 
Genes found to be associated with unfavorable (pFDR < 0.05, HR > 1) or favorable BCR prognosis (pFDR < 0.05, HR < 1) in all three cohorts were considered as standalone markers of BCR prognosis listed in __Supplementary Table S\@ref(tab:tab-uni-bcr)__.

@@

suppl_tab$uni_bcr %>% 
  filter(`Gene symbol` %in% reduce(uni_cut$common_significant, union)) %>% 
  arrange(`Association with BCR risk`, `Gene symbol`, Cohort) %>% 
  relocate(`Association with BCR risk`, `Gene symbol`, Cohort) %>% 
  flextable %>% 
  merge_v(1:2) %>% 
  italic(j = 2) %>% 
  set_widths(c(2, 2, 2, 1.8, rep(2.4, 2), 2.2, 2.3, rep(1.7, 2))) %>% 
  footnote(1, 7, 
           value = as_paragraph('Harazd ratio (HR) with 95% confidence intervals (CI).'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 9, 
           value = as_paragraph("C-index: Harrel's concordance index, a measure of model accuracy. High values are expected for a highly accurate model; concordance index = 0.5 is expected for random predictions."), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  footnote(1, 10, 
           value = as_paragraph('IBS: Integrated Brier Score, a metric of model calibration. Low values are expected for a well calibrate model. Intergrated Brier score = 0.25 is expected for random predictions.'), 
           part = 'header', 
           ref_symbols = 'c') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tab$bcr_eval) %>% 
  merge_v(1:2) %>% 
  set_widths(c(3.5, 2.7, 3.5, rep(2.5, 2))) %>% 
   footnote(1, 1, 
           value = as_paragraph('SVM: Support Vector Machines; GBM: Gradient Boosted Machines.'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1:18, 1, 
           value = as_paragraph('Explanatory factors: expression levels of the collagen-related transcripts.'), 
           part = 'body', 
           ref_symbols = 'b') %>% 
  footnote(19:21, 1, 
           value = as_paragraph('Explanatory factors: pathological tumor stage, ISUP grade, and log2 expression of the PSA coding gene KLK3 in the tumor tissue.'), 
           part = 'body', 
           ref_symbols = 'c') %>% 
   footnote(22:24, 1, 
           value = as_paragraph('Explanatory factors: pathological tumor stage, ISUP grade, and log2 expression of the PSA coding gene KLK3 in the tumor tissue, log2 expression of the collagen-related transcripts.'), 
           part = 'body', 
           ref_symbols = 'd') %>% 
  footnote(1, 4, 
           value = as_paragraph("C-index: Harrel's concordance index, a measure of model accuracy. High values are expected for a highly accurate model; concordance index = 0.5 is expected for random predictions."), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  footnote(1, 5, 
           value = as_paragraph('IBS: Integrated Brier Score, a metric of model calibration. Low values are expected for a well calibrated model. Intergrated Brier score = 0.25 is expected for random predictions.'), 
           part = 'header', 
           ref_symbols = 'c') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tab$os_eval) %>% 
  set_widths(c(3.5, 2.7, rep(2.5, 2))) %>% 
  merge_v(1) %>% 
  footnote(1, 3, 
           value = as_paragraph("C-index: Harrell's concordance index, a measure of model accuracy. High values are expected for a highly accurate model; concordance index = 0.5 is expected for random predictions."), 
           part = 'header', 
           ref_symbols = 'b') %>% 
  footnote(1, 4, 
           value = as_paragraph('IBS: Integrated Brier Score, a metric of model calibration. Low values are expected for a well calibrate model. Intergrated Brier score = 0.25 is expected for random predictions.'), 
           part = 'header', 
           ref_symbols = 'c') %>% 
  theme_vanilla

@@

_(A) Numeric metrics of survival model performance, Harrell's concordance index (C-index, measure of model accuracy) and Integrated Brier Score (IBS, measure of calibration, low values are characteristic for well calibrated models), are presented in a dot plot. Each point represents a single GBM model, point color codes for the model type. Models in the same cohort are connected with lines. Note the substantial improvement of the GBM model accuracy and calibration upon inclusion of the collagen-related transcript expression levels in the explanatory variable set in the pooled GEO and DKFZ cohorts._

@@

_(A) Metrics of performance of the survival models, Harrell's concordance index (C-index, measure of model accuracy) and Integrated Brier Score (IBS, measure of model calibration, low values are characteristic for good calibration), are presented in dot plots. Dashed lines represent C-index and IBS values expected for random death risk prediction. Note the superior accuracy and calibration of the GBM model in the validation collectives._
